---
title: "Introduction to StatsAid"
author: "Leran Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatsAid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# StatsAid: A Comprehensive Data Analysis Toolkit

StatsAid is designed to streamline and enhance the data analysis workflow for researchers. This vignette introduces you to the main features and functions of the package.

## Installation

```{r, eval=FALSE}
# Install from GitHub
# install.packages("devtools")
devtools::install_github("username/StatsAid-R")
```

## Basic Usage

Let's start by loading the package and creating some sample data to demonstrate StatsAid's capabilities:

```{r}
library(StatsAid)

# Create sample data with various data types and some missing values
set.seed(123)
sample_data <- data.frame(
  age = c(25, 30, 35, 40, NA, 45, 50, 55, 60, 65),
  weight = c(70, 75, NA, 85, 90, 65, 80, 75, 70, 85),
  height = c(170, 175, 180, 185, 175, 165, NA, 175, 180, 170),
  gender = factor(c("M", "F", "M", "F", "M", "F", "M", "F", "M", "F")),
  smoker = c(TRUE, FALSE, TRUE, FALSE, NA, FALSE, TRUE, FALSE, TRUE, FALSE),
  income = c(50000, 60000, 55000, 70000, 65000, 75000, 60000, 80000, 90000, 150000)
)
```

## Data Exploration

The `explore()` function provides a comprehensive overview of your dataset:

```{r}
# Get data overview
overview <- explore(sample_data)
print(overview)
```

## Missing Data Analysis

StatsAid offers sophisticated tools for analyzing missing data patterns:

```{r}
# Analyze missing data patterns
missing_analysis <- analyze_missing_patterns(sample_data, plot = FALSE)
print(missing_analysis)
```

## Visualizing Data

StatsAid provides several visualization functions to help you understand your data:

```{r, fig.width=7, fig.height=5}
# Plot missing data
plot_missing_bar(sample_data)
```

Let's visualize the distributions of our variables:

```{r, fig.width=7, fig.height=5}
# Get distribution plots for numeric variables
distribution_plots <- plot_distributions(sample_data, max_cols = 3)
# Display the first numeric plot
distribution_plots$numeric$age
```

And let's look at correlations between numeric variables:

```{r, fig.width=7, fig.height=6}
# Create correlation matrix
plot_correlation_matrix(sample_data)
```

Detecting outliers is also straightforward:

```{r, fig.width=7, fig.height=5}
# Create boxplots for outlier detection
plot_outliers(sample_data)
```

## Testing for Normality

StatsAid provides tools for testing the normality of your variables:

```{r}
# Test normality of numeric variables
normality_results <- test_normality(sample_data)
print(normality_results)
```

## Getting Preprocessing Suggestions

Based on its analysis, StatsAid can suggest appropriate preprocessing steps:

```{r}
# Get preprocessing suggestions
preprocessing_suggestions <- suggest_preprocessing(sample_data)
print(preprocessing_suggestions)
```

## Statistical Model Suggestions

StatsAid can also suggest appropriate statistical models based on your study design:

```{r}
# Get model suggestions based on a specific study design
model_suggestions <- suggest_models(sample_data, study_design = "cross_sectional")
print(model_suggestions)
```

## Automated Reporting

Finally, StatsAid can generate comprehensive reports with a single function call:

```{r, eval=FALSE}
# Generate a complete report
create_report(sample_data, 
              title = "Sample Data Analysis", 
              file = "sample_report.html")
```

## Conclusion

StatsAid provides a complete toolkit for data exploration, visualization, preprocessing, and analysis. By automating many routine tasks and providing intelligent suggestions, it helps researchers spend less time on data wrangling and more time on interpretation and discovery.

For more details on each function, refer to the function documentation.